\textbf{Modelling Neuroplasticity: Using Machine Learning to Learn About TMS Data}

### 2023-06-12 paper/paper.tex
.

\begin{remark} 
    $\forall x: x \in \mathbb{R}^+:\delta(x) \geq \rho(x)$. (For a proof of this
    property, consult the appendix.) 
\end{remark}

@@

\begin{remark}
    Let $\pi$ denote the coefficient traditionally used for estimating the
    relative amplitude between test and paired pulses. In accordance to what was
    described in the second paragraph of Section $4$,

@@

    (For a proof, consult the appendix.)
\end{remark}

@@

\subsection{Generalizing to many subjects}

\begin{definition}
    Let $\textbf{x} \in \mathbb{R}^j$. Then we define $T(\textbf{x}) := \begin{bmatrix} 
        \rho(x_1) & \ldots & \rho(x_j)
    \end{bmatrix}^\intercal $ and $R(\textbf{x}) := \begin{bmatrix} 
        \delta(x_1) & \ldots & \delta(x_j) 
    \end{bmatrix}^\intercal $.
\end{definition}

\begin{theorem}
    The mappings $T, R$ are linear transformations.
\end{theorem}

Let $k \in \mathbb{N}$ denote the number of experimental subjects in an
experiment, to each of whom $n, m$ paired and test pulses were elicited,
respectively.

@@

\begin{definition}
    Let $\mu^{(t)}_i$ be average test-pulse response of the $i$th subject. Then
    we define
    $\textbf{M}^{k \times k}$ a diagonal matrix with $\textbf{M}_{(ii)} =
    \frac{1}{\mu^{(t)}_{i}}$.
\end{definition}

\begin{theorem}
    The row-vectors of the matrix $\textbf{X}_\rho = \textbf{M}\textbf{P}$ are the
    vectors $T(\textbf{x}^{(1)}), \ldots, T(\textbf{x}^{(k)})$.
\end{theorem}

Similarly, if we let $\textbf{M'}$ be a diagonal matrix such that
$\textbf{M'}_{ii} = \mu^{(t^{-1})}_i$, where $\mu^{(t^{-1})}_i$ denotes the
average \textit{inverse} test-pulse response of the $i$th subject, we come to
the following result.

\begin{theorem}
    The row-vectors of the matrix $\textbf{X}_\delta = \textbf{M'}\textbf{P}$ 
    are the vectors $R(\textbf{x}^{(1)}), \ldots,
    R(\textbf{x}^{(k)})$.
\end{theorem}

@@

We have expanded $\rho, \delta$ to higher dimensions for the purpose of
providing a theoretical framework of their application to larger data sets and
many experimental subjects. However, it is important to note that the matrix
representations here presented only make sense under the assumption that, on
each subject, none of $n$ paired pulses were anomalous, and hence all can be
safely included in the model. Such assumption rarely holds in reality, where it
is usual to excluded some pulses due to the presence of artifacts. There are
many ways to deal with this situation in the implementation of our model---the
safest being the direct application of $T$ and $R$ to the data vectors---. Thus,
more than serving the algorithmic implementation of the model, which may
prescind from them, these matrices provide insight into the nature of the
transformations involved in the model.

>>>>

\begin{theorem} 
    $\forall x: x \in \mathbb{R}^+:\delta(x) \geq \rho(x)$. (For a proof of this
    property, consult the appendix.) 
\end{theorem}

@@

\begin{theorem}
    Let $\pi$ denote the coefficient traditionally used for estimating the
    relative amplitude between test and paired pulses. In accordance to what was
    described in the second paragraph of Section $4$,

@@

    (For a proof, consult the appendix.)
\end{theorem}

@@

\subsection{Generalizing to multiple subjects}

\begin{definition}
    Let $\textbf{x} \in \mathbb{R}^j$ with $j \in \mathbb{N}$. Then $T:
    \mathbb{R}^j \to \mathbb{R}^j, R : \mathbb{R}^j \to \mathbb{R}^j$ are the
    linear transformations defined as

    $T(\textbf{x}) := \begin{bmatrix} 
        \rho(x_1) & \ldots & \rho(x_j)
    \end{bmatrix}^\intercal $ and $R(\textbf{x}) := \begin{bmatrix} 
        \delta(x_1) & \ldots & \delta(x_j) 
    \end{bmatrix}^\intercal $.
\end{definition}

It is trivial to show that $T$ and $R$ are linear mappings (consult the
Appendix). Now let $k \in \mathbb{N}$ denote the number of experimental subjects
in an experiment, to each of whom $n, m$ paired and test pulses were elicited,
respectively.

@@

\begin{definition}
    Let $\mu^{(t)}_i$ be average test-pulse response of the $i$th subject. Let
    $\mu^{(t)^{-1}}_i$ be the average \textit{reciprocal} test-pulse response of
    the $i$th subject. Then $\textbf{M}^{k \times k}$ is a diagonal matrix with
    $\textbf{M}_{(ii)} := \frac{1}{\mu^{(t)}_{i}}$, and $\textbf{M'}^{~ k \times
    k}$ is a diagonal matrix with $\textbf{M'}_{ii} := \mu^{(t^{-1})}_i$.
\end{definition}

\begin{theorem}
    The row-vectors of $\textbf{X}_\rho = \textbf{M}\textbf{P}$ are the
    vectors $T(\textbf{x}^{(1)}), \ldots, T(\textbf{x}^{(k)})$, and
    the row-vectors of $\textbf{X}_\delta = \textbf{M'}\textbf{P}$ 
    are the vectors $R(\textbf{x}^{(1)}), \ldots,
    R(\textbf{x}^{(k)})$.
\end{theorem}

@@

We have expanded $\rho, \delta$ to higher dimensions for the purpose of
providing a theoretical framework of their application to larger data sets and
many experimental subjects. However, it is important to note that the matrix
representations here presented only make sense under the assumption that, on
each subject, none of $n$ paired pulses were anomalous, and hence all can be
safely included in the model. Such assumption rarely holds in reality, where it
is usual to excluded some pulses due to the presence of artifacts. There are
many ways to deal with this situation in the implementation of our model---the
safest being the direct application of $T$ and $R$ to the data vectors---. Thus,
more than serving the algorithmic implementation of the model, which may
prescind from them, these matrices provide insight into the exact nature of the
transformations involved in the model.
